---
title: "Overview of Gameday"
author: "Yi Sui"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

## Introduction

You are really a big hocky fan! When you're in your office writing `R` code and suddenly 
have the urge to check whether your NHL team has a game today and whether your NHL team 
won the game on a particular date. Now instead of using 15 minutes browsing the lastest 
news on your favorite hockey webpage, you can now ask `R` directly with the help
of this `gameday` package.

The `gameday` package provides a convenient way to know whether a specified NHL team has a 
game on a specified date and scores of all the games on a specified date through `R` 
instead of the traditional way -- searching on the Internet. 


## Load the package 

In order to use the functions in the `gameday` packages, we need first load the package
by using 
```{r}
library(gameday)
```


## Function gday(team, date)

This function gives the option to check whether a specified NHL team has a 
game on a specified date. 

The function has two arguments: `team` and `date`. __NOTE: Both these two argument 
should be input as a string, i.e. with quotation mark around the input argument, and 
the date should be in the right date format, i.e. "yyyy-mm-dd".__
In default, the `team` is set to be "Canucks" and `date` is set to be today's date. 
For example, we can check whether "Canucks" has a game tonight with:
```{r}
# check whether "Canucks" has a game today
gday()
```

If we want to check whether "Bruins" has a game on "2014-11-02" or not, we can do:
```{r}
# check whether "Bruins" has a game on "2014-11-02"
gday("Bruins", "2014-11-02")
```

__NOTE: This function is not case sensitive.__ For example: we can either use 
"Canucks" or "canucks" to check for the game information.
```{r}
# apply gday() to "Canucks"
gday("Canucks")

# apply gday() to "canucks"
gday("canucks")

# confirm gday() is not case sensitive
identical(gday("Canucks"), gday("canucks"))
```

__NOTE: If all the sudden, you forgot the name of team asking by the city name also works in `gday()`.__ For example, instead of asking "canucks", we can also use "Vancouver".

```{r}
# apply gday() to "canucks"
gday("canucks")

# apply gday() to "Vancouver"
gday("Vancouver")

# confirm asking by the city name also works
identical(gday("canucks"), gday("Vancouver"))
```

## Function scores(date)

This function gives the option to display the scores of all the games on a 
specified date as a `data.frame`. 

The function only takes one argument `date`. Again, the date should be in the right date 
format, i.e. "yyyy-mm-dd". For example, we can check the scores for the games
happen on "2014-11-19":

```{r, results='asis'}
# look up the scores for the games on "2014-11-19"
knitr::kable(scores("2014-11-19"))
```

__NOTE: `knitr` is used above to make a nice looking table.__

We can see that it returns a `data.frame` six columns. The first column shows the name of 
the home team, the second column for the name of the away team. The third column gives 
the score for the home team, while the score for the away team is given on the forth 
column. The column "stage" shows the current stage of the game and the 
last column gives a friendly note about whether you will be able to watch the game on 
"gamecenter" or not.

__NOTE: There are three possible outcomes in the "stage" column. If a game haven't 
started yet, in the "stage" column it will show the game starting time in EST. If the 
game is in progress, it will show which period the game is at and the remaining time for
this period. If a game has finished, it will show "Final".__

Since we can use the function `score(date)` to get a very informative `data.frame` with 
all the scores for the games at a perticular date, we can go from this 
`data.frame` to gain some insight. For example, we can use the `data.frame` to list all 
winning teams on "2014-11-18". In order to do that, we will need our old friend `dplyr`.
```{r}
# load package "dplyr"
suppressPackageStartupMessages(library(dplyr))
```

Now we can use `dplyr` to find the winning teams on "2014-11-18".
```{r}
# look for the winning teams  on "2014-11-18"
scores_data <- scores("2014-11-18")

scores_data %>%
	mutate(winning_team = ifelse(home_score > away_score, as.character(home), 
															as.character(away))) %>%
	select(winning_team)
```

We can compare the "winning_team" with our original `data.frame` "scores_data" and see 
all the teams display here are indeed the winning teams on "2014-11-18".

